---
title: "Survey results"
output: html_notebook
---


```{r libraries}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(highcharter)
library(ggthemes)
library(plotly)
```

```{r setup}
# Add thousand seperator
hcoptslang <- getOption("highcharter.lang")
hcoptslang$thousandsSep <- "."
options(highcharter.lang = hcoptslang)

raw_results <- read.csv(file = 'Datasets/survey.csv')
```

# Amount of users per video streaming service grouped on age
```{r}
groups <- c("Under 18 years old", "18-24", "25-34", "35-44", "45-54", "55-64", "65 years old or above")

# Create individual rows based on column
df <- separate_rows(raw_results, What.video.streaming.services.do.you.currently.use., convert = TRUE, sep=";")

# Remove left/right whitespace
df$What.video.streaming.services.do.you.currently.use. <- trimws(df$What.video.streaming.services.do.you.currently.use., which = c("both"))

# Get services that have more than 1 vote
popular_services <- df %>%
    group_by(What.video.streaming.services.do.you.currently.use.) %>%
    summarise(n=n()) %>%
    filter(n > 1)

# Group on video streaming services and summarise n amount
df <- df %>% 
  group_by(What.is.your.age., What.video.streaming.services.do.you.currently.use.) %>% 
  summarise(amount=n()) %>%
  filter(What.video.streaming.services.do.you.currently.use. != "") %>%
  filter(What.video.streaming.services.do.you.currently.use. %in% popular_services$What.video.streaming.services.do.you.currently.use.)

plot <- ggplot(df, aes(x = fct_relevel(What.is.your.age., groups), y = What.video.streaming.services.do.you.currently.use., fill = amount)) + 
  geom_tile() +
  geom_text(aes(label = round(amount, 1))) +
  scale_fill_gradient(low = "white", high = "red") +
  labs(title = "Usage of Video Streaming Services by age", x = "Age groups", y = "Video streaming services", fill="Amount of users") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))

ggplotly(plot)
```

# Proportion of Respondents Who Subscribed to a Video Streaming Service for Specific Content grouped

```{r}
# Create individual rows based on column
data <- separate_rows(raw_results, What.video.streaming.services.do.you.currently.use., convert = TRUE, sep=";")

# Remove left/right whitespace
data$What.video.streaming.services.do.you.currently.use. <- trimws(data$What.video.streaming.services.do.you.currently.use., which = c("both"))

# Group on video streaming services and summarise n amount
data <- data %>% 
  group_by(Have.you.ever.subscribed.to.a.video.streaming.service.solely.to.watch.a.specific.show.or.movie., What.video.streaming.services.do.you.currently.use.) %>% 
  summarise(amount=n()) %>%
  arrange(desc(amount)) %>%
  filter(amount > 1) %>%
  filter(What.video.streaming.services.do.you.currently.use. != "")

hchart(
  data,
  "column",
  hcaes(x= reorder(What.video.streaming.services.do.you.currently.use., amount), y=amount, group=Have.you.ever.subscribed.to.a.video.streaming.service.solely.to.watch.a.specific.show.or.movie.)
) |>
  hc_title(text = "Respondents who subscribed to a video streaming service for specific content by video streaming service") |>
  hc_yAxis(title = list(text = "Amount")) |>
  hc_xAxis(title = list(text = "")) |>
  hc_add_theme(hc_theme_google()) |>
  hc_plotOptions(series = list(
  borderWidth= 0,
  dataLabels = list(
    enabled = TRUE,
    color = "black"
  )))
```

```{r}
# Create individual rows based on column
data <- raw_results # separate_rows(raw_results, What.video.streaming.services.do.you.currently.use., convert = TRUE, sep=";")

# Group on video streaming services and summarise n amount
data <- data %>% 
  group_by(Have.you.ever.subscribed.to.a.video.streaming.service.solely.to.watch.a.specific.show.or.movie., What.is.your.age.) %>% 
  summarise(amount=n()) %>%
  arrange(desc(amount)) %>%
  filter(amount > 1)

hchart(
  data,
  "column",
  hcaes(x= reorder(What.is.your.age., amount), y=amount, group=Have.you.ever.subscribed.to.a.video.streaming.service.solely.to.watch.a.specific.show.or.movie.)
) |>
  hc_title(text = "Respondents who subscribed to a video streaming service for specific content by age") |>
  hc_yAxis(title = list(text = "Amount")) |>
  hc_xAxis(title = list(text = "")) |>
  hc_add_theme(hc_theme_google()) |>
  hc_plotOptions(series = list(
  borderWidth= 0,
  dataLabels = list(
    enabled = TRUE,
    color = "black"
  )))
```

# Factors Considered Most Important When Choosing a Video Streaming Service

```{r}
df <- raw_results %>% 
  pivot_longer(cols = names(raw_results)[4:8],
                    values_to = "value") %>%
  select(What.is.your.age., name, value)

ggplot(df, aes(x=name, y=value)) + 
  geom_boxplot(fill="slateblue", alpha=0.2) + 
  labs(title = "Factors Considered Most Important When Choosing a Video Streaming Service", x = "Factors", y = "Importance (ranked from 1 to 5)") +
  scale_x_discrete(labels = c('Availability on \n multiple devices', 'Content selection', 'Layout and \n easy of use', 'Price', 'Video quality'))
  # + facet_wrap(vars(What.is.your.age.))
```





# Reasons for Cancelling Video Streaming Service Subscriptions

```{r}
# Create individual rows based on column
data <- separate_rows(raw_results, Have.you.ever.canceled.a.video.streaming.service.subscription..If.so..why., convert = TRUE, sep=";")

# Remove left/right whitespace
data$Have.you.ever.canceled.a.video.streaming.service.subscription..If.so..why. <- trimws(data$Have.you.ever.canceled.a.video.streaming.service.subscription..If.so..why., which = c("both"))

# Group on video streaming services and summarise n amount
data <- data %>% 
  group_by(What.is.your.age., Have.you.ever.canceled.a.video.streaming.service.subscription..If.so..why.) %>% 
  summarise(amount=n()) %>%
  arrange(desc(amount)) %>%
  filter(Have.you.ever.canceled.a.video.streaming.service.subscription..If.so..why. != "")

hchart(
  data,
  "column",
  hcaes(x = Have.you.ever.canceled.a.video.streaming.service.subscription..If.so..why., y = amount, group = What.is.your.age.)
) |>
  hc_title(text = "Reasons for Cancelling Video Streaming Service Subscriptions") |>
  hc_yAxis(title = list(text = "Amount")) |>
  hc_xAxis(title = list(text = "")) |>
  hc_add_theme(hc_theme_google()) |>
  hc_plotOptions(series = list(
  borderWidth= 0,
  dataLabels = list(
    enabled = TRUE,
    color = "black"
  )))
```

```{r}
# Create individual rows based on column
df <- separate_rows(raw_results, What.video.streaming.services.do.you.currently.use., convert = TRUE, sep=";")

# Remove left/right whitespace
df$What.video.streaming.services.do.you.currently.use. <- trimws(df$What.video.streaming.services.do.you.currently.use., which = c("both"))

# Get services that have more than 1 vote
popular_services <- df %>%
    group_by(What.video.streaming.services.do.you.currently.use.) %>%
    summarise(n=n()) %>%
    filter(n > 1)

# Group on video streaming services and summarise n amount
df <- df %>% 
  group_by(How.satisfied.are.you.with.the.overall.value.of.the.video.streaming.services.you.currently.use., What.video.streaming.services.do.you.currently.use.) %>% 
  summarise(amount=n()) %>%
  filter(What.video.streaming.services.do.you.currently.use. != "") %>%
  filter(What.video.streaming.services.do.you.currently.use. %in% popular_services$What.video.streaming.services.do.you.currently.use.)

hchart(
  df,
  "column",
  hcaes(
    x = What.video.streaming.services.do.you.currently.use., 
    y = amount,
    group=How.satisfied.are.you.with.the.overall.value.of.the.video.streaming.services.you.currently.use.
  )
) |>
  hc_title(text = "Satisfaction ratings by Video Streaming Services") |>
  hc_yAxis(title = list(text = "Rating %")) |>
  hc_xAxis(title = list(text = "")) |>
  hc_add_theme(hc_theme_google()) |>
  hc_plotOptions(
    column = list(stacking = "percent"),
    series = list(
      borderWidth= 0,
      dataLabels = list(
        enabled = FALSE, # Note set this to TRUE to see numbers
        color = "white"
  )))
```


























# Video streaming services by age  
Create a bar chart to show the percentage of respondents who use each video streaming service. Perform cross-tabulations to see how the usage of different services varies across different age groups

# Stacked bar chart met (have you ever subscribed to a video streaming service solely to....) per video streaming service (Original content)
# Gemiddelde tevredenheid met huidige streaming services 
# Gemiddelde leeftijd met streaming services (Door middel van mean or ordinal values)


# Amount of respondents by age group

```{r}
data <- raw_results %>% 
  group_by(What.is.your.age.) %>% 
  summarise(amount=n())

groups <- c("Under 18 years old", "18-24", "25-34", "35-44", "45-54", "55-64", "65 years old or above")

data <- data %>%
  slice(match(groups, What.is.your.age.))
  
hchart(
  data,
  "column",
  hcaes(x = What.is.your.age., y = amount),
  name = "Amount of respondents by age group",
  groupPadding = 0
) |>
  hc_title(text = "Amount of respondents by age group") |>
  hc_yAxis(title = list(text = "Total respondents")) |>
  hc_xAxis(title = list(text = "Age groups")) |>
  hc_add_theme(hc_theme_google()) |>
  hc_plotOptions(series = list(
  borderWidth= 0,
  dataLabels = list(
    enabled = TRUE,
    color = "black"
  )))
```

# Streaming services

```{r}
# Create individual rows based on column
data <- separate_rows(raw_results, What.video.streaming.services.do.you.currently.use., convert = TRUE, sep=";")

# Remove left/right whitespace
data$What.video.streaming.services.do.you.currently.use. <- trimws(data$What.video.streaming.services.do.you.currently.use., which = c("both"))

# Group on video streaming services and summarise n amount
data <- data %>% 
  group_by(What.video.streaming.services.do.you.currently.use.) %>% 
  summarise(amount=n()) %>%
  arrange(desc(amount)) %>%
  filter(amount > 1) %>%
  filter(What.video.streaming.services.do.you.currently.use. != "")

hchart(
  data,
  "column",
  hcaes(x = What.video.streaming.services.do.you.currently.use., y = amount),
  name = "",
  groupPadding = 0
) |>
  hc_title(text = "") |>
  hc_yAxis(title = list(text = "")) |>
  hc_xAxis(title = list(text = "")) |>
  hc_add_theme(hc_theme_google()) |>
  hc_plotOptions(series = list(
  borderWidth= 0,
  dataLabels = list(
    enabled = TRUE,
    color = "black"
  )))
```

# Are you interested in subscribing to a video streaming service that offers a pay per view pricing for individual movies and TV shows rather than a monthly subscription fee?

```{r}
data <- raw_results %>% group_by(Are.you.interested.in.subscribing.to.a.video.streaming.service.that.offers.a.pay.per.view.pricing.for.individual.movies.and.TV.shows..rather.than.a.monthly.subscription.fee.) %>% summarise(amount=n())

hchart(
  data,
  "column",
  hcaes(x = Are.you.interested.in.subscribing.to.a.video.streaming.service.that.offers.a.pay.per.view.pricing.for.individual.movies.and.TV.shows..rather.than.a.monthly.subscription.fee., y=amount),
  name = "Amount of respondents",
  groupPadding = 0
) |>
  #hc_title(text = "") |>
  hc_yAxis(title = list(text = "Total respondents")) |>
  hc_xAxis(title = list(text = "")) |>
  hc_add_theme(hc_theme_google()) |>
  hc_plotOptions(series = list(
  borderWidth= 0,
  dataLabels = list(
    enabled = TRUE,
    color = "black"
  )))
```